Discussion

### 2023-03-08 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
last limitations

Third, it is a major limitation that participants had to use three given ER strategies.

>>>>

Third, it is a major limitation that participants had to use three given ER strategies.
It could be that some of the participants did not implement or were used to any of the three strategies in everyday life.
So it may be that none of the strategies has a really high subjective value for the person.
However, strategies for attentional deployment, cognitive change, and response modulation were chosen that meta-analytically proved to be most effective [@Webb2012]. 
Related to that, individual SVs of each person have to be interpreted with caution. 
They depend on the specific context: The stimulus material presented and the strategies that are compared with each other.
Thus, it could be that SVs for one ER strategy would be higher or lower when using other stimuli or valences of stimuli and other comparison strategies.
That is because the computation of SVs is inseparable form the other SVs.

Fourth, the highest value during the discounting paradigm was set to 2 € as fixed value.
Participants should imagine that this was the amount of money they would get when they would repeat this strategy.
One might argue that 2 € as an incentive to repeat an entire block is quite low.
However, we chose this amount because, first, we have followed the original paradigm of Westbrook[@Westbrook2013].
Further it was shown that
